### 2013-06-06 menger.tex
Relatively compact results

  \begin{proof}
  Assume $\sigma(\mc{U}_0,\dots,\mc{U}_{k-1},n)$ is a winning $k$-Markov strategy. Define the $2$-Markov strategy $\tau(\mc{U},\mc{V},n)$ so that it contains $\sigma(\mc{W}_0,\dots,\mc{W}_{k-1},m)$ for the following conditions on $(\mc{W}_0,\dots,\mc{W}_{k-1},m)$:
    \begin{itemize}
    \item Each $\mc{W}_i \in \{\mc{U},\mc{V}\}$
    \item $m \leq (n+1)k$; in particular, for $i<k$, 
      \[
        \sigma(\mc{W}_0,\dots,\mc{W}_{k-1},(n+1)k+i)
        \subseteq 
        \tau(\mc{U},\mc{V},n+1) 
      \]
    \end{itemize}

@@

  Due to Telgarski in ``On Games of Topsoe'' (along with $\sigma$-compact implying $F\markwin \mengame{X}$).

  \begin{theorem}
    For metrizable $X$, $X$ is $\sigma$-compact if and only if $F \win \mengame{X}$ if and only if $F\markwin \mengame{X}$.
  \end{theorem}

  We adapt this result for regular spaces.

  \begin{lemma}
    Let $\sigma(\mc{U}, n)$ be a winning Markov strategy for $F$ in $\mengame{X}$, and $\mathfrak{C}$ collect all open covers of $X$. Then for
      \[
        C_n = \bigcap_{\mc{U}\in\mathfrak{C}} \overline{\bigcup\sigma(\mc{U},n)}
      \]
    and
      \[
        D_n = \bigcap_{\mc{U}\in\mathfrak{C}} \bigcup\sigma(\mc{U},n)
      \]
    it follows that $\bigcup_{n<\omega} C_n = \bigcup_{n<\omega} D_n = X$.
  \end{lemma}

  \begin{proof}
    Observe $D_n \subseteq C_n$. Suppose that $x \not\in D_n = \bigcap_{\mc{U}\in\mathfrak{C}} \bigcup\sigma(\mc{U},n)$ for any $n<\omega$. Then for each $n$, pick $\mc{U}_n\in\mathfrak{C}$ such that $x\not\in \bigcup\sigma(\mc{U}_n,n)$. Then $\sigma$ does not defeat the play $\mc{U}_0,\mc{U}_1,\dots$ since the $\sigma(\mc{U}_n,n)$ do not cover $x$, contradiction.
  \end{proof}

  \begin{theorem}
    For regular spaces $X$, $X$ is $\sigma$-compact if and only if $F \markwin \mengame{X}$.
  \end{theorem}

  \begin{proof}
    The reverse implication has already been shown. To complete the proof, we look to Scheepers for inspiration.

    Let $\sigma(\mathcal{U},n)$ be a winning Markov strategy for $F$ in $\mengame{X}$. Let $\mathfrak{C}$ collect all open covers of $X$. Define
      \[
        C_n = \bigcap_{\mc{U}\in\mathfrak{C}} \overline{\bigcup\sigma(\mc{U},n)}
      \]
    as in the previous lemma. Note that $\bigcup_{n<\omega} C_n = X$, and we will show each $C_n$ is compact as it is $H$-closed.

    Let $\mc{U}$ be an open cover of $C_n$, and $\mc{V}$ be a cover of $X\setminus C_n$ by open sets whose closures are disjoint from $C_n$ (possible by regularity).

    Since $\mc{U}\cup\mc{V}$ covers $X$, $\overline{\bigcup\sigma(\mc{U}\cup\mc{V},n)} \supseteq C_n$. Furthermore, if $\mc{F} = \sigma(\mc{U}\cup\mc{V},n)\setminus \mc{V}$, then $\overline{\bigcup\mc{F}} \supseteq C_n$ (the closures of sets in $\mc{V}$ missed $C_n$). Thus $\mc{F}$ witnesses that $C_n$ is $H$-closed.
  \end{proof}

@@

  There cannot be a winning Markov strategy $\sigma(\mc{U},n)$, however. Define 
      \[
        D_n = \bigcap_{\mc{U}\in\mathfrak{C}} \bigcup\sigma(\mc{U},n)
      \]
  where $\mathfrak{C}$ is the collection of open covers of $R$. For any $x_0,x_1,\dots \in R$, we may define the open cover $\mc{U} = \{R \setminus \{x_i: i \not= n\} : n < \omega \}$, and observe that $\bigcup \sigma(\mc{U},n) \supseteq D_n$ cannot contain every $x_i$. Thus $D_n$ is finite, but since the previous lemma requires $\bigcup_{n<\omega} D_n = R$ if $\sigma$ is a winning strategy, there exists a counter to $\sigma$.
  \end{proof}

@@

    Let $\mathfrak{C}$ collect all the open covers of $X$. We say $X$ is \scish if there exists a fuction $f:\mathfrak{C}\times\omega\to\mc{P}(X)$ such that:
      \begin{itemize}
        \item $f(\mc{V},n)$ is $\mc{V}$-compact
        \item $f(\mc{V},n)\subseteq f(\mc{V},n+1)$
        \item $\bigcup_{n<\omega}f(\mc{V},n)=X$
        \item The set
          \[
            g(\mc{U},\mc{V},n) = \bigcup_{m\geq n} f(\mc{U},m)\setminus ( f(\mc{U},m-1)\cup f(\mc{V},m))
          \]
         is $\mc{V}$-compact
      \end{itemize}
  \end{definition}

@@

>>>>

  \begin{proof}
  Assume $\sigma(\mc{U}_0,\dots,\mc{U}_{k-1},n)$ is a winning $k$-Markov strategy. Define the $2$-Markov strategy $\tau(\mc{U},\mc{V},n)$ so that it contains $\sigma(\mc{W}_0,\dots,\mc{W}_{k-2},\mc{V},m)$ for the following conditions on $\mc{W}_0,\dots,\mc{W}_{k-2},m$:
    \begin{itemize}
    \item Each $\mc{W}_i \in \{\mc{U},\mc{V}\}$
    \item $m \leq (n+1)k$; in particular, for $i<k$, 
      \[
        \sigma(\mc{W}_0,\dots,\mc{W}_{k-2},\mc{V},(n+1)k+i)
        \subseteq 
        \tau(\mc{U},\mc{V},n+1) 
      \]
    \end{itemize}

@@

  Telgarski showed in ``On Games of Topsoe'' that a metrizable space is $\sigma$-compact if and only if there exists a winning strategy for $F$ in the Menger game, and Scheepers gave a more direct proof later. We slightly generalize Scheeper's proof.

  \begin{definition}
    A space $X$ is $H$-closed if for every open cover of $X$, there exists a finite subset of the cover whose union is dense in $X$.
  \end{definition}

  \begin{proposition}
    For regular spaces, $X$ is $H$-closed if and only if $X$ is compact.
  \end{proposition}

  \begin{proof}
    TODO: this
  \end{proof}

  \begin{definition}
    A set $R\subseteq X$ is relatively compact to the topological space $X$ if for every open cover of the entire space $X$, there is a finite subcover of the set $R$.
  \end{definition}

  \begin{proposition}
    Every subset of a compact set is relatively compact to the entire space.
  \end{proposition}

  \begin{proposition}
    If $X$ is regular, then $Y$ is relatively compact if and only if $\cl{Y}$ is compact.
  \end{proposition}

  \begin{proof}
    The reverse implication is trivial.

    Assume $Y$ is relatively compact, let $\mc U$ be an open cover of $\cl Y$, and let $\mc V$ be an open cover of $X\setminus\cl Y$ such that the closure of each member also misses $\cl Y$ (possible by regularity).

    Let $\mc W\subseteq \mc U \cup \mc V$ be a finite subcover of $Y$, and note $\cl{\bigcup\mc W} \supseteq \cl Y$. If $\mc F = \mc W \setminus \mc V$, then $\cl{\bigcup\mc F} \supseteq \cl Y$ as well. Thus $\bigcup\mc F$ is dense in $\cl Y$, showing $\cl Y$ is $H$-closed and thus compact.
  \end{proof}

  \begin{theorem}
    For metrizable $X$, the following are equivalent:
      \begin{enumerate}[(a)]
        \item $X$ is $\sigma$-compact
        \item $X$ is $\sigma$-(relatively compact)
        \item $F \win \mengame{X}$
        \item $F\markwin \mengame{X}$
      \end{enumerate}
  \end{theorem}

  \begin{proof}
    We've seen $(a) \Rightarrow (d)$, and $(d)\Rightarrow(c)$ is trivial. We may see $(b)\Rightarrow(a)$ since for regular spaces, the closure of a relatively compact set is compact.

    To prove $(c)\Rightarrow(b)$, let $\sigma(\mc{U}_0,\dots,\mc{U}_{n-1})$ be a winning strategy for $F$, and observe that since $X$ is second-countable, we may assume all covers are countable. Let $\mathfrak{C}$ be the collection of all countable covers of $X$. We define $R_s,\mc{U}_s$ for $s\in\omega^{<\omega}$ as follows:
      \begin{itemize}
        \item $\ds R_\emptyset = \bigcap_{\mc{U}\in\mathfrak{C}} \left(\bigcup \sigma(\mc{U})\right)$
        \item Note that there are only countably many distinct finite subsets $\sigma(\mc{U})$ of the countable collection $\mathfrak{C}$. Thus define each $\mc U_{\<n\>}$ so that
          \[
            R_\emptyset = 
            \bigcap_{n<\omega}\left(\bigcup\sigma(\mc{U}_{\<n\>})\right)
          \]
        \item $\ds R_s = \bigcap_{\mc{U}\in\mathfrak{C}} \left(\bigcup \sigma(\mc{U}_{s\rest1},\mc{U}_{s\rest2},\dots,\mc{U}_s,\mc{U})\right)$
        \item Again, note that there are only countably many distinct finite subsets $\sigma(\mc{U}_{s\rest1},\mc{U}_{s\rest2},\dots,\mc{U}_s,\mc{U})$ of the countable collection $\mathfrak{C}$. Thus define each $\mc U_{s\concat\<n\>}$ so that 
          \[
            R_s = 
            \bigcap_{n<\omega} \left(\bigcup \sigma(\mc{U}_{s\rest1},\mc{U}_{s\rest2},\dots,\mc{U}_s,\mc{U}_{s\concat\<n\>})\right)
          \]
      \end{itemize}

    We quickly confirm that each $R_s$ is relatively compact as for each open cover $\mc{U}$ of $X$ we have the finite subcover $\sigma(\mc{U}_{s\rest1},\mc{U}_{s\rest2},\dots,\mc{U}_s,\mc{U})$ of $R_s$.

    Finally, we claim that $X = \bigcup_{s\in\omega^{<\omega}} R_s$. If not, let $x$ be missed by every $R_s$, and define $f\in\omega^\omega$ such that $x\not\in \bigcup\sigma(\mc{U}_{f\rest1},\dots,\mc{U}_{f\rest n})$ for any $n$. Then $\mc{U}_{f\rest1},\mc{U}_{f\rest2},\dots$ is a counter to the winning strategy $\sigma$, a contradiction.
  \end{proof}

  We generalize this result for non-metric spaces.

  \begin{lemma}
    Let $\sigma(\mc{U}, n)$ be a winning Markov strategy for $F$ in $\mengame{X}$, and $\mathfrak{C}$ collect all open covers of $X$. Then for
      \[
        R_n = \bigcap_{\mc{U}\in\mathfrak{C}} \bigcup\sigma(\mc{U},n)
      \]
    it follows that $R_n$ is relatively compact to $X$, and $\bigcup_{n<\omega} R_n = X$.
  \end{lemma}

  \begin{proof}
    First, we see that $\sigma(\mc{U},n)$ witnesses the relative compactness of $R_n$. Suppose that $x \not\in R_n = \bigcap_{\mc{U}\in\mathfrak{C}} \bigcup\sigma(\mc{U},n)$ for any $n<\omega$. Then for each $n$, pick $\mc{U}_n\in\mathfrak{C}$ such that $x\not\in \bigcup\sigma(\mc{U}_n,n)$. Then $\sigma$ does not defeat the play $\mc{U}_0,\mc{U}_1,\dots$ since the $\sigma(\mc{U}_n,n)$ do not cover $x$.
  \end{proof}

  \begin{theorem}
    A space $X$ is $\sigma$-(relatively compact) if and only if $F \markwin \mengame{X}$.
  \end{theorem}

  \begin{proof}
    For the forward implication, let $X=\bigcup_{n<\omega}R_n$ for $R_n$ relatively compact, and define $\sigma(\mc U,n)$ to be a finite subcover of $R_n$. The previous lemma proves the other direction.
  \end{proof}

  \begin{corollary}
    For regular spaces $X$, the following are equivalent:
      \begin{enumerate}[(a)]
        \item $X$ is $\sigma$-compact
        \item $X$ is $\sigma$-(relatively compact)
        \item $F \markwin \mengame{X}$
      \end{enumerate}
  \end{corollary}

@@

  There cannot be a winning Markov strategy $\sigma(\mc{U},n)$, however. Define 
      \[
        R_n = \bigcap_{\mc{U}\in\mathfrak{C}} \bigcup\sigma(\mc{U},n)
      \]
  where $\mathfrak{C}$ is the collection of open covers of $R$. For any $x_0,x_1,\dots \in R$, we may define the open cover $\mc{U} = \{R \setminus \{x_i: i \not= n\} : n < \omega \}$, and observe that $\bigcup \sigma(\mc{U},n) \supseteq R_n$ contains only finitely many $x_i$. Thus $R_n$ is finite, but since the previous lemma requires $\bigcup_{n<\omega} R_n = R$ if $\sigma$ is a winning strategy, there exists a counter to $\sigma$.
  \end{proof}

@@

    Let $\mathfrak{C}$ collect all the open covers of $X$. We say $X$ is \scish if there exists a function $f:\mathfrak{C}\times\omega\to\mc{P}(X)$ such that:
      \begin{itemize}
        \item $f(\mc{V},n)$ is $\mc{V}$-compact
        \item $f(\mc{V},n)\subseteq f(\mc{V},n+1)$
        \item $\bigcup_{n<\omega}f(\mc{V},n)=X$
        \item The set
          \[
            g(\mc{U},\mc{V},n) = \bigcup_{m\geq n} f(\mc{U},m)\setminus ( f(\mc{U},m-1)\cup f(\mc{V},m))
          \]
         is $\mc{V}$-compact
      \end{itemize}
  \end{definition}

@@

  \newpage

  \begin{definition}
    $X$ is \textbf{Rothberger} if for all open covers $\mathcal{U}_0,\mathcal{U}_1,\dots$ there exist open sets $U_n\in \mathcal{U}_n$ such that $\{U_n:n<\omega\}$ is a cover of $X$.
  \end{definition}

  \begin{proposition}
    Rothberger $\Rightarrow$ Menger
  \end{proposition}

  \begin{definition}
    In the two-player game $\rothgame{X}$ player $C$ chooses open covers $\mathcal{U}_n$ of $X$, followed by player $O$ choosing an open set $U_n\in\mathcal{U}_n$. $O$ wins if $\{U_n:n<\omega\}$ is a cover of $X$.
  \end{definition}

  \begin{theorem}
    $X$ is Rothberger if and only if $C\not\win\rothgame{X}$.
  \end{theorem}

  \begin{proof}
    Due to Pawlikowski
  \end{proof}
